Lessons learned from bugs in models of human history

### 2020-05-22 paper.tex
Minor fiddling

>>>>

\aprcomment{
In particular, we do not observe large differences in mean predicted risk 
across populations (Fig.~\ref{fig:prs}C,D), present in data and simulations from~\citet{martin2017human}.
Thus, a model with continental-scale demographic structure, highly polygenic architecture, and
neutral evolution does not appear to explain the observed large directional biases
in mean predicted risk.
}
